---
title: "RNA2-pt2"
author: "Sofia Salazar"
date: "2022-11-10"
output: html_document
---

## Setup

```{bash}
qlogin
cd /mnt/Citosina/amedina/ssalazar/meta/RNA2/fastq_files
module load r/4.0.2
R
```

## Obtaining the count matrixes for each studies

For SRP111941, as it is a single-ended library, we only get the count matrix from a single folder, however, for the other remaining studies, we have pair ended libraries and we have three folders with counts, first for the paired reads, for the forward unpaired reads and the reverse unpaired reads which were generated through the trimming step.

```{r}
# SRP111941
setwd("/mnt/Citosina/amedina/ssalazar/meta/RNA2/fastq_files/SRP111941/STAR_output")
files <- dir(pattern="ReadsPerGene.out.tab") # count files

f1 <- read.table(file=files[1], sep = "\t", header = F, as.is = T)
f2 <- read.table(file=files[2], sep = "\t", header = F, as.is = T)
counts <- c()
for( i in seq_along(files) ){
  x <- read.table(file=files[i], sep="\t", header=F, as.is=T)
  counts <- cbind(counts, x[,2])
}

head(counts)
tail(counts)
dim(counts)
class(counts)
class(x) # the original count tab file from star
counts <- as.data.frame(counts)
# Assigning the rows a name (the ID)
rownames(counts) <- x[,1]

# Assinging the columns a name
# set the column names
colnames(counts) <- sub(".fastq.*", "", files)

# saving the counts
save(counts, file = "/mnt/Citosina/amedina/ssalazar/meta/RNA2/fastq_files/SRP111941/SRP111941-counts.RData")
```


```{r}
# SRP296987
setwd("/mnt/Citosina/amedina/ssalazar/meta/RNA2/fastq_files/SRP296987/STAR_output_pe")
files <- dir(pattern="ReadsPerGene.out.tab") # count files

counts <- c()
for( i in seq_along(files) ){
  x <- read.table(file=files[i], sep="\t", header=F, as.is=T)
  counts <- cbind(counts, x[,2])
}
# se1
setwd("/mnt/Citosina/amedina/ssalazar/meta/RNA2/fastq_files/SRP296987/STAR_output_se1")
files <- dir(pattern="ReadsPerGene.out.tab") # count files
counts1 <- c()
for( i in seq_along(files) ){
  x <- read.table(file=files[i], sep="\t", header=F, as.is=T)
  counts1 <- cbind(counts1, x[,2])
}
# se2 
setwd("/mnt/Citosina/amedina/ssalazar/meta/RNA2/fastq_files/SRP296987/STAR_output_se2")
files <- dir(pattern="ReadsPerGene.out.tab") # count files
counts2 <- c()
for( i in seq_along(files) ){
  x <- read.table(file=files[i], sep="\t", header=F, as.is=T)
  counts2 <- cbind(counts2, x[,2])
}

head(counts)
tail(counts)
dim(counts)
class(counts)
class(x) # the original count tab file from star

# sum counts from unpaired and paired
counts<-as.matrix(counts)
counts1<-as.matrix(counts1)
counts2<-as.matrix(counts2)

total.counts <- (counts + counts1)
total.counts <- as.data.frame(total.counts + counts2)


# Assigning the rows a name (the ID)
rownames(total.counts) <- x[,1]

# Assinging the columns a name
# set the column names
colnames(total.counts) <- sub("_.*", "", files)

# saving the counts
save(total.counts, file = "/mnt/Citosina/amedina/ssalazar/meta/RNA2/SRP296987-counts.RData")
```

```{r}
# SRP311059
setwd("/mnt/Citosina/amedina/ssalazar/meta/RNA2/fastq_files/SRP311059/STAR_output_pe")
files <- dir(pattern="ReadsPerGene.out.tab") # count files

counts <- c()
for( i in seq_along(files) ){
  x <- read.table(file=files[i], sep="\t", header=F, as.is=T)
  counts <- cbind(counts, x[,2])
}
# se1
setwd("/mnt/Citosina/amedina/ssalazar/meta/RNA2/fastq_files/SRP311059/STAR_output_se1")
files <- dir(pattern="ReadsPerGene.out.tab") # count files
counts1 <- c()
for( i in seq_along(files) ){
  x <- read.table(file=files[i], sep="\t", header=F, as.is=T)
  counts1 <- cbind(counts1, x[,2])
}
# se2 
setwd("/mnt/Citosina/amedina/ssalazar/meta/RNA2/fastq_files/SRP311059/STAR_output_se2")
files <- dir(pattern="ReadsPerGene.out.tab") # count files
counts2 <- c()
for( i in seq_along(files) ){
  x <- read.table(file=files[i], sep="\t", header=F, as.is=T)
  counts2 <- cbind(counts2, x[,2])
}

head(counts)
tail(counts)
dim(counts)
class(counts)
class(x) # the original count tab file from star

# sum counts from unpaired and paired
counts<-as.matrix(counts)
counts1<-as.matrix(counts1)
counts2<-as.matrix(counts2)

tail(counts,1)
tail(counts1,1)
total.counts <- (counts + counts1)
tail(total.counts,1)
total.counts <- as.data.frame(total.counts + counts2)
tail(counts2,1)
tail(total.counts,1)

# Assigning the rows a name (the ID)
rownames(total.counts) <- x[,1]

# Assinging the columns a name
# set the column names
colnames(total.counts) <- sub("_.*", "", files)

# saving the counts
save(total.counts, file = "/mnt/Citosina/amedina/ssalazar/meta/RNA2/SRP311059-counts.RData")
```


```{r}
# SRP322015
setwd("/mnt/Citosina/amedina/ssalazar/meta/RNA2/fastq_files/SRP322015/STAR_output_pe")
files <- dir(pattern="ReadsPerGene.out.tab") # count files

counts <- c()
for( i in seq_along(files) ){
  x <- read.table(file=files[i], sep="\t", header=F, as.is=T)
  counts <- cbind(counts, x[,2])
}
# se1
setwd("/mnt/Citosina/amedina/ssalazar/meta/RNA2/fastq_files/SRP322015/STAR_output_se1")
files <- dir(pattern="ReadsPerGene.out.tab") # count files
counts1 <- c()
for( i in seq_along(files) ){
  x <- read.table(file=files[i], sep="\t", header=F, as.is=T)
  counts1 <- cbind(counts1, x[,2])
}
# se2 
setwd("/mnt/Citosina/amedina/ssalazar/meta/RNA2/fastq_files/SRP322015/STAR_output_se2")
files <- dir(pattern="ReadsPerGene.out.tab") # count files
counts2 <- c()
for( i in seq_along(files) ){
  x <- read.table(file=files[i], sep="\t", header=F, as.is=T)
  counts2 <- cbind(counts2, x[,2])
}

head(counts)
tail(counts)
dim(counts)
class(counts)
class(x) # the original count tab file from star

# sum counts from unpaired and paired
counts<-as.matrix(counts)
counts1<-as.matrix(counts1)
counts2<-as.matrix(counts2)

tail(counts,1)
tail(counts1,1)
total.counts <- (counts + counts1)
tail(total.counts,1)
total.counts <- as.data.frame(total.counts + counts2)
tail(counts2,1)
tail(total.counts,1)

# Assigning the rows a name (the ID)
rownames(total.counts) <- x[,1]

# Assinging the columns a name
# set the column names
colnames(total.counts) <- sub("_.*", "", files)

# saving the counts
save(total.counts, file = "/mnt/Citosina/amedina/ssalazar/meta/RNA2/SRP322015-counts.RData")
```

```{r}
# SRP168421
setwd("/mnt/Citosina/amedina/ssalazar/meta/RNA2/fastq_files/SRP168421/STAR_output_pe")
files <- dir(pattern="ReadsPerGene.out.tab") # count files

counts <- c()
for( i in seq_along(files) ){
  x <- read.table(file=files[i], sep="\t", header=F, as.is=T)
  counts <- cbind(counts, x[,2])
}
# se1
setwd("/mnt/Citosina/amedina/ssalazar/meta/RNA2/fastq_files/SRP168421/STAR_output_se1")
files <- dir(pattern="ReadsPerGene.out.tab") # count files
counts1 <- c()
for( i in seq_along(files) ){
  x <- read.table(file=files[i], sep="\t", header=F, as.is=T)
  counts1 <- cbind(counts1, x[,2])
}
# se2 
setwd("/mnt/Citosina/amedina/ssalazar/meta/RNA2/fastq_files/SRP168421/STAR_output_se2")
files <- dir(pattern="ReadsPerGene.out.tab") # count files
counts2 <- c()
for( i in seq_along(files) ){
  x <- read.table(file=files[i], sep="\t", header=F, as.is=T)
  counts2 <- cbind(counts2, x[,2])
}

head(counts)
tail(counts)
dim(counts)
class(counts)
class(x) # the original count tab file from star

# sum counts from unpaired and paired
counts<-as.matrix(counts)
counts1<-as.matrix(counts1)
counts2<-as.matrix(counts2)

tail(counts,1)
tail(counts1,1)
total.counts <- (counts + counts1)
tail(total.counts,1)
total.counts <- as.data.frame(total.counts + counts2)
tail(counts2,1)
tail(total.counts,1)

# Assigning the rows a name (the ID)
rownames(total.counts) <- x[,1]

# Assinging the columns a name
# set the column names
colnames(total.counts) <- sub("_.*", "", files)

# saving the counts
save(total.counts, file = "/mnt/Citosina/amedina/ssalazar/meta/RNA2/SRP168421-counts.RData")
```

## Output

The output files are in `/mnt/Citosina/amedina/ssalazar/meta/RNA2/SRP*-counts.RData`

